|

### 2025-01-29 doc/paper.qmd
prep

**Step 2: Data Preparation**  
If a firm has missing values for any of the Earnings Per Share Report Date fields (`item5901`–`item5904`), it does not meet the criteria set by @ball_how_2008 and was excluded from the sample.

>>>>

The pull step results into three comprehensive datasets: DS table with 27,950,012, Link table with 77,944, WSCP table with 1,942,202 observations.

**Step 2: Data Preparation**

If a firm has missing values for any of the Earnings Per Share Report Date fields (`item5901`–`item5904`), it does not meet the criteria set by @ball_how_2008 and was excluded from the sample.
